Learning causal features with double regression

### 2019-04-11 paper/paper.tex
Done.
Added blah.
Added maths (1), pseudo inverse derivation

\author{%
  Jean-Remi King\\
  Facebook AI\\
  \texttt{email} \\
  \And
  Fran\c{c}ois Charton\\
  Facebook AI\\
  \texttt{fcharton@fb.com}\\
  \And
  David Lopez-Paz\\
  Facebook AI\\
  \texttt{fcharton@fb.com}
}

@@

\section{Problem formulation}
\begin{equation}
    Y = F(SX + N)
    \label{eq:model}
\end{equation}

\subsection{Consistency proof}

\begin{equation}
\begin{aligned}
\min_G \left \| X-YG \right \| &= \min_G \left \| X - (XSF+NF)G\right\| \\
&{}= \min_G \left \| X - XSFG\right\|  + \left \| NFG \right \| \\
\end{aligned}
\end{equation}

Given that :
\begin{equation}
\mathop{\mathbb{E}}[N]=0
\end{equation}

and
\begin{equation}
\left \| X-XSFG \right \| \leq \left \| X \right \| \cdot  \left \| I-SFG \right \| \\
\end{equation}

Then
\begin{equation}
\min_G \left \| X-YG \right \| = \min_G \left \| I -SFG\right\| \\
\Rightarrow \hat  G= (SF)^{\dagger}
\end{equation}

\subsection{LS from X to Y\^{G}}

\begin{equation}
\begin{aligned}
\min_H \left \| Y \hat G - XH \right \| &= \min_H \left \| (XSF+NF) \hat G - XH \right \| \\
&= \min_H \left \| XSF \hat G - XH \right \| \\
&= \min_H \left \| SF \hat G - H \right \| \\
&= \min_H \left \| SF (SF)^{\dagger} - H \right \| \\
\end{aligned}
\end{equation}

Under the assumptions that S is an orthogonal projection
\begin{equation}
    S = S^2, S=S^T, S^{\dagger} = S
\end{equation}

And under the extra assumptions that :

\begin{equation}
(SF)^{\dagger} = F^{\dagger} S^{\dagger}
\end{equation}

Then,

\begin{equation}
\begin{aligned}
\min_H \left \| SF (SF)^{\dagger} - H \right \| &= \min_H \left \| SFF^{\dagger}S^{\dagger} - H \right \| \\
&= \min_H \left \| SS^{\dagger} - H \right \| \\
&= \min_H \left \| SS - H \right \| \\
&= \min_H \left \| S - H \right \|\\
\Rightarrow \hat H = S
\end{aligned}
\end{equation}

>>>>

\author{%
  Jean-Remi King\\
  Facebook AI\\
  \texttt{email} \\
  \And
  Fran\c{c}ois Charton\\
  Facebook AI\\
  \texttt{fcharton@fb.com}\\
  \And
  David Lopez-Paz\\
  Facebook AI\\
  \texttt{dlp@fb.com}
}

@@

\section{Problem formulation}
Our problem may be formulated as
\begin{equation}
    Y = F(EX + N)
    \label{eq:model}
\end{equation}
where F is an unknown matrix, presumably full or high rank, corresponding to the measurement apparatus, E is a low rank transformation carried on the features (X), and N a noise term, centred but not necessarily gaussian or diagonal.

The first regression (X from Y), amounts to finding
\begin{equation}
\begin{aligned}
\min_G \left \| X-GY \right \|^2 &= \min_G \left \| X - GF(EX+N)\right\|^2 \\
&{}= \min_G \left \| (I-GFE)X\right\| ^2 + \left \| GFN\right \| ^2\\
&{}\leq \min_G \left \| I-GFE\right\| ^2 \left \| X\right\| ^2 + k\left \| G\right \| ^2\\ 
\end{aligned}
\end{equation}
since N is centred, and with k a positive constant which depends on the variance of FN.

This amounts to finding the minimal norm generalized inverse of FE, or its Moore-Penrose inverse
\begin{equation}
\hat  G= (FE)^{\dagger}
\end{equation}

The second regression is from X to the predicted value of X in the above, or $\hat G  Y$

\begin{equation}
\begin{aligned}
\min_H \left \| (FE)^{\dagger}Y - HX \right \|^2 &= \min_H \left \| (FE)^{\dagger}F(EX+N) - HX \right \|^2 \\
&= \min_H \left \| ((FE)^{\dagger}(FE)-H)X \right \| ^2 + \left \| (FE)^{\dagger}FN \right \| ^2\\
&= \min_H \left \| ((FE)^{\dagger}(FE)-H)X \right \| ^2\\
\end{aligned}
\end{equation}

Therefore, under the hypothese that N is centred, our regression method estimates 
\begin{equation}
\begin{aligned}
\hat H =(FE)^{\dagger}(FE)
\end{aligned}
\end{equation}

For any matrix A, $A^\dagger A$ is the orthogonal projector over Img(A'), and $I-A^\dagger A$ the orthogonal projector over Ker(A).

If E selects some features of X (ie Ex=0 on any unselected feature, and E full ranked over the set of selected features) and if F is full rank over the subspace spanned by the features selected by E, then 
\begin{equation}
\begin{aligned}
Ker(FE) = Ker(E)  
\end{aligned}
\end{equation}
$I - \hat H$ is the projector over Ker(E), the diagonal matrix that spans the unselected features, and $\hat H$ is the diagonal matrix corresponding to the selected features.

Under such hypotheses, $\hat H$ retrieves the features of X that have a causal influence on Y, and should do it in a fairly resilient way, since it is diagonal, and all its eigenvalues (0 or 1) are well separated.

\section{Estimator, and relation with Canonical Component Analysis}
